---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# redmineR

`redmineR` is an R API client for the [Redmine](http://www.redmine.org) project
management system.

## Installation

To install the package from GitHub, you can use devtools:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("openanalytics/redmineR")
```

To get a quick package overview, run:
```{r}
library(redmineR)
?redmineR
```

## Example

You can quickly get a working Redmine demo environment to try `redmineR`
by filling a simple form at http://m.redmine.org.
After that log-in to the administration panel, and click "Load default
configuration". Then make sure "Enable REST web service" is checked in the
"Settings".

As mentioned on the website,

> Please, remember that this demo environment is provided with absolutely NO
WARRANTY and for TESTING PURPOSE ONLY. The access to this environment can be
disabled and your data deleted at any time, so don't store sensitive information
here. 

The following example shows an interaction with such a demo environment.
Feel free to use authentication details provided, but there is no guarantee they
will remain functional.

### Set authentication for the current session  

```{r auth}
Sys.setenv("REDMINE_URL" = "http://rredmine.m.redmine.org")
Sys.setenv("REDMINE_TOKEN" = "b91fe6803b09b27b068ee02157db2a8100d52f81")
```

### See what is already there
```{r list}
redmine_projects()

redmine_users()
```

### Create a new project
```{r project}
(newProjectId <- redmine_create_project(name = "testProject",
    identifier = "test-project", description = "project to testthings",
    enabled_module_names = c("files", "issue_tracking", "repository", 
        "time_tracking", "wiki")))

# trivial update
redmine_update_project(newProjectId, description = "project to test things")
```

### List projects again
```{r list2}
redmine_projects()
```

or:
```{r list3}
redmine_list_projects()
```

### Create an issue
```{r issue}
projectID <- redmine_search_id("testProject", 
    endpoint = "projects")

# now create issue
issueID <- redmine_create_issue(
    project_id = projectID, 
    subject = "test task", 
    description = "test description"
)
```

### See its details
```{r issueInfo}
redmine_show_issue(issueID, include = "all")
```

### Clean up
```{r clean}
redmine_delete_issue(issueID)
redmine_delete_project(projectID)
```
