---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# redmineR

`redmineR` is an R API client for the [Redmine](http://www.redmine.org) project
management system.

## Installation

To install the package from GitHub, you can use package `remotes` (or
`devtools`):

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("openanalytics/redmineR")
```

To get a quick package overview, run:
```{r}
library(redmineR)
?redmineR
```

## Authentication

Authentication is performed using API key, which can be obtained by accessing
`[redmine_server_URL]/my/account`. Note that REST API should be enabled by
the server administrator. 

The easiest way to provide the API key to `redmineR` is to define environment
variables `REDMINE_URL` and `REDMINE_TOKEN` inside your `.Renviron` file. If
these variables are not defined, you will be prompted to enter url/token with
the first `redmineR` request (this would be saved for the current session
only). 

## Example

You can quickly get a working Redmine demo environment to try `redmineR`
by filling a simple form at http://m.redmine.org.
After that log-in to the administration panel, and click "Load default
configuration". Then make sure "Enable REST web service" is checked in the
"Settings".

As mentioned on the website,

> Please, remember that this demo environment is provided with absolutely NO
WARRANTY and for TESTING PURPOSE ONLY. The access to this environment can be
disabled and your data deleted at any time, so don't store sensitive information
here. 

The following example shows an interaction with such a demo environment.
Feel free to use authentication details provided, but there is no guarantee they
will remain functional.

### Set authentication for the current session  

```{r auth}
Sys.setenv("REDMINE_URL" = "http://rredmine.m.redmine.org")
Sys.setenv("REDMINE_TOKEN" = "b91fe6803b09b27b068ee02157db2a8100d52f81")
```

### See what is already there
```{r list}
redmine_projects()

redmine_users()
```

### Create a new project
```{r project}
(newProjectId <- redmine_create_project(name = "testProject",
    identifier = "test-project", description = "project to testthings",
    enabled_module_names = c("files", "issue_tracking", "repository", 
        "time_tracking", "wiki")))

# trivial update
redmine_update_project(newProjectId, description = "project to test things")
```

### List projects again
```{r list2}
redmine_projects()
```

or:
```{r list3}
redmine_list_projects()
```

### Create an issue
```{r issue}
projectID <- redmine_search_id("testProject", 
    endpoint = "projects")[1]

# now create issue
issueID <- redmine_create_issue(
    project_id = projectID, 
    subject = "test task", 
    description = "test description"
)
```

### See its details
```{r issueInfo}
redmine_show_issue(issueID, include = "all")
```

### Use custom queries

Using custom search queries is a powerful feature of redmine. It is not
currently possible to create new queries with Rest API, but it is possible to
list them and use when searching for issues, as demonstrated below.

We have created a new user and a custom query for them that would list all
"Bugs" that are not "Closed".


```{r queries}
# change user account
Sys.setenv("REDMINE_TOKEN" = "6d6af23f4089fe902d875a5521ffae17d756d1a1")

# list existing queries (`name` can also be specified for further filtering),
# and save ID of the first one
queryId <- redmine_search_id(endpoint = "queries")[1] 

# now list issues following this query call.
redmine_issues(query_id = queryId)
```

### Clean up
```{r clean}
# need to have admin rights
Sys.setenv("REDMINE_TOKEN" = "b91fe6803b09b27b068ee02157db2a8100d52f81")

redmine_delete_issue(issueID)
redmine_delete_project(projectID)
```

